Classical density functional theory for the square-well liquid

### 2014-03-28 papers/square-well-liquid/paper.tex
add a bit about the gsigma (section still needs to be added) Tested on darcy. Took 0:20.28.

@@

\fixme{We have introduced an approximation to the pair distribution
  function...}

>>>>

The approximation for the averaged pair distribution $g_\sigma(\rr)$
is from Schulte \emph{et al.}~\cite{schulte2012using}.  We will here
summarize the key results needed to implement this approximation.

@@

\fixme{We have introduced an approximation to the pair distribution
  function above... here we discuss an implementation of thermodynamic
  perturbation theory for an inhomogeneous system using this pair
  distribution function.}
